Graph Testing

### 2019-08-05 notes/graph_testing.tex
updated graph testing document

\section{Fixed graph testing.}

@@

To more explicitly specify the critical radius $\epsilon: \norm{\beta}_2 \geq \epsilon$, we will need to make an assumption on the relation between $N(C)$ and $C$. In particular, let $C = C^*$, where
\begin{equation*}
C^* = c\frac{(C_n n^{s/d})^{4s/(4s + d)}}{n^{s/d}}.
\end{equation*}
for some $c$ constant in $n$. We will assume the following bound on $N(C^*)$:
\begin{enumerate}[label=(A\arabic*)]
	\item Tail decay:
	\label{asmp:tail_decay}
	\begin{equation*}
	N(C^*) \leq (C^*)^{d/s}n
	\end{equation*}
\end{enumerate}

\begin{corollary}
	\label{cor:critical_radius}
	Fix $b \geq 1$, assume \ref{asmp:tail_decay}. Then, for any $C_n > 0$
	\begin{equation*}
	\sup_{\substack{\beta \in \mathcal{S}_d^{s}(C_n), \\ \norm{\beta}_2/n \geq \epsilon}} \Ebb_{\beta}(1 - \phi_{C^{\star}}) \leq \frac{2}{b^2} + \frac{2}{b\sqrt{N(C^{\star})}}
	\end{equation*}
	for every $\epsilon > 0$ such that 
	\begin{equation*}
	\epsilon^2 \geq (2b + 1) \left(\frac{(C_n n^{s/d})^{2d/(4s + d)}}{n}\right).
	\end{equation*}
\end{corollary}
\begin{proof}
	First, we verify that $\epsilon^2 \geq 2b\sqrt{2N(C^*)/n^2} + C_n^2/n(C^*)^2$. By Assumption \ref{asmp:tail_decay} and the choice of $C^{\star}$, we have
	\begin{equation*}
	N(C^*) \leq (C^*)^{d/s}n = (C_n n^{s/d})^{4d/(4s + d)}
	\end{equation*}
	and therefore
	\begin{equation*}
	2b\sqrt{\frac{N(C^*)}{n^2}} \leq \frac{2b}{n} (C_n n^{s/d})^{2d/(4s+d)}
	\end{equation*}
	Moving on to the second term, we have
	\begin{align*}
	\frac{C_n^2}{n(C^{\star})^2} & = \frac{C_n^2n^{2s/d}}{n(C_nn^{s/d})^{8s/(4s+d)}} \\
	& = \frac{C_n^{2d/(4s + d)}n^{(s/d)2d/(4s + d)}}{n} \\
	& = \frac{(C_n n^{s/d})^{2d/(4s + d)}}{n}
	\end{align*}
	and therefore $\epsilon \geq 2b\sqrt{2N(C^*)/n^2} + C_n^2/n(C^*)^2$. As a result, by Lemma \ref{lem:type_II} for any $\beta \in \mathcal{S}^s_d(C_n)$ such that $\norm{\beta}/n \geq \epsilon$, 
	\begin{equation*}
	\Ebb_{\beta}(1 - \phi_{C^{\star}}) \geq \frac{2}{b^2} + \frac{2}{b\sqrt{2N(C^{\star})}}.
	\end{equation*}
\end{proof}

@@

In the following result, we prove that for an appropriate choice of threshold $C$ and radius $r$, the test $\phi_C$ achieves (nearly) minimax-optimal rates. Let
\begin{equation*}
C^{\star} = \frac{\left(n^{1 + s/d}r^{d/2 + s}\right)^{4s/(4s + d)}}{n^{s/d}}.
\end{equation*}

\begin{theorem}
	\label{thm:sobolev_testing_rate}
	Let $b \geq 1$ be a fixed constant, and let $s = 1$. For any sequence $r_n$ such that $(\log n/n)^{1/d}r \to \infty$, there exists a constant $c$ which depends only on $d$ and $L$ such that
	\begin{equation}
	\label{eqn:sobolev_testing_rate_1}
	\mathcal{R}_{\epsilon}(\phi_{C^{\star}}; \mathcal{W}^{s,2}(\mathcal{D};L)) \leq c_1\left(\frac{1}{b^2} + \frac{1}{b\sqrt{N(C^{\star})}}\right) + o(1)
	\end{equation}
	for every $\epsilon$ such that
	\begin{equation}
	\label{eqn:sobolev_testing_rate}
	\epsilon^2 \geq c_2 b \left(\frac{(b n^{1 + s/d}r^{d/2 + s})^{2d/(4s + d)}}{n}\right).
	\end{equation}
\end{theorem}

\subsection{Proof of Theorem \ref{thm:sobolev_testing_rate}}
Our goal is to upper bound
\begin{equation*}
\mathcal{R}_{\epsilon}(\phi_{C^{\star}}; W^{1,2}(\mathcal{D};L)) = \Ebb_{f = 0}(\phi_{C^{\star}}) + \sup_{f \in W^{1,2}(\mathcal{D};L): \norm{f}_2 > \epsilon} \Ebb_{f}(1 - \phi_{C^{\star}})
\end{equation*}
By Lemma \ref{lem:type_I_error}, we immediately have $\Ebb_{f = 0}(\phi_{C^{\star}}) \leq 1/b^2$, and we turn to the worst-case type II error. Fix any $f \in W^{1,2}(\mathcal{D};L)$ such that $\norm{f}_2 > \epsilon$, and let $\beta$ be the length-$n$ random vector with $j$th entry $\beta_j = f(x_j)$. Consider the following events:
\begin{enumerate}[label=(E\arabic*)]
	\item 
	\label{event:discrete_sobolev_norm}
	Discrete Sobolev norm of $\beta$: There exists a constant $c_1$ which depends only on $p_{\max}$ and $d$ such that
	\begin{equation*}
	\norm{B^{(s)}\beta}_2^2 \leq c_1 b^2 n^2 r^{d + 2s} 
	\end{equation*}
	\item 
	\label{event:eigenvalue_tail_decay}
	Eigenvalue tail decay:
	\begin{equation*}
	N(C^{\star}) \leq n(C^{\star})^{d/s}.
	\end{equation*}
	\item 
	\label{event:l2_norm}
	$L_2$ norm of $\beta$:
	\begin{equation*}
	\frac{\norm{\beta}_2^2}{n} \geq \frac{1}{2}\epsilon^2.
	\end{equation*}
\end{enumerate}

Each of these events happen with high probability as $n \to \infty$.
\begin{lemma}
	\label{lem:high_probability_events}
	With probability at least $1 - \frac{1}{b^2}$ as $n \to \infty$,
	\begin{equation}
	\label{eqn:discrete_sobolev_norm}
	\norm{B\beta}_2^2 \leq c_1 b^2 n^2 r^{d + 2}.
	\end{equation}

	With probability tending to one as $n \to \infty$,
	\begin{equation}
	\label{eqn:eigenvalue_tail_decay}
	N(C^{\star}) \leq n(C^{\star})^{d/s}.
	\end{equation}

	\textcolor{red}{$L_2$ norm}.
\end{lemma}
In the following subsections, we prove Lemma \ref{lem:high_probability_events}. First, we show that Theorem \ref{thm:sobolev_testing_rate} is a simple consequence of Lemma \ref{lem:high_probability_events} along with our previous work. Let $\mathcal{A}_f$ be the set of $X$ such that \ref{event:discrete_sobolev_norm}, \ref{event:eigenvalue_tail_decay}, and \ref{event:l2_norm} all occur, for the given choice of $f$. We have that for $C_n := c_1bnr^{d/2 + s}$, the event \ref{event:discrete_sobolev_norm} implies $\beta \in \mathcal{S}_d^s(C_n)$. Therefore, by \ref{event:l2_norm},
\begin{equation}
\label{eqn:sobolev_testing_rate_2}
\Ebb_f(1 - \phi_{C^*}) \leq \sup_{\substack{\beta \in \mathcal{S}_d^{s}(C_n), \\ \norm{\beta}_2/n \geq \epsilon^2/2}} \Ebb_{\beta}(1 - \phi_{C^{\star}}) + \Pbb(\mathcal{A}_f).
\end{equation}
Observe the following: 
\begin{itemize}
	\item \textcolor{red}{$C^{\star} = (C_n n^{s/d})^{4s/(4s+d)}/n^{s/d}$},
	\item The event \ref{event:eigenvalue_tail_decay} is exactly \ref{asmp:tail_decay}, and 
	\item For an appropriate choice of $c_2$, by hypothesis
	\begin{equation*}
	\epsilon^2/2 \geq (2\sqrt{2}b + 1) \left(\frac{(C_n n^{s/d})^{2d/(4s + d)}}{n}\right)
	\end{equation*}
\end{itemize}
Therefore we may apply Corollary \ref{cor:critical_radius}, and obtain
\begin{equation*}
\sup_{\substack{\beta \in \mathcal{S}_d^{s}(C_n), \\ \norm{\beta}_2/n \geq \epsilon^2/2}} \Ebb_{\beta}(1 - \phi_{C^{\star}}) \leq \frac{2}{b^2} + \frac{2}{b\sqrt{N(C^{\star})}},
\end{equation*}
and along with \eqref{eqn:sobolev_testing_rate_2} and Lemma \ref{lem:high_probability_events}, this shows
\begin{equation*}
\Ebb_f(1 - \phi_{C^*}) \leq \frac{3}{b^2} + \frac{2}{b\sqrt{N(C^{\star})}} + o(1).
\end{equation*}

@@

>>>>

\section{Fixed graph testing.}
\label{sec:fixed_graph_testing}

@@

To more explicitly specify the critical radius $\epsilon: \norm{\beta}_2 \geq \epsilon$, we will need to make an assumption on the relation between $N(C)$ and $C$. In particular, let $C = C^*$, where
\begin{equation*}
\label{eqn:C_star}
C^* = c\frac{(C_n n^{s/d})^{4s/(4s + d)}}{n^{s/d}}.
\end{equation*}
for some $c$ constant in $n$. We will assume the following bound on $N(C^*)$:
\begin{enumerate}[label=(A\arabic*)]
	\item Tail decay:
	\label{asmp:tail_decay}
	\begin{equation*}
	N(C^*) \leq (C^*)^{d/s}n
	\end{equation*}
\end{enumerate}

\begin{corollary}
	\label{cor:critical_radius}
	Fix $b \geq 1$, assume \ref{asmp:tail_decay}. Then, for any $C_n > 0$
	\begin{equation*}
	\sup_{\substack{\beta \in \mathcal{S}_d^{s}(C_n), \\ \norm{\beta}_2/\sqrt{n} \geq \epsilon}} \Ebb_{\beta}(1 - \phi_{C^{\star}}) \leq \frac{2}{b^2} + \frac{2}{b\sqrt{N(C^{\star})}}
	\end{equation*}
	for every $\epsilon > 0$ such that 
	\begin{equation*}
	\epsilon^2 \geq (2bc^{d/2s} + c^{-2}) \left(\frac{(C_n n^{s/d})^{2d/(4s + d)}}{n}\right),
	\end{equation*}
	where $c$ is the same constant as appears in \eqref{eqn:C_star}.
\end{corollary}
\begin{proof}
	Our goal is to verify that, when
	\begin{equation*}
	\frac{\norm{\beta}_2^2}{n} \geq (2bc^{d/2s} + c^{-2}) \left(\frac{(C_n n^{s/d})^{2d/(4s + d)}}{n}\right)
	\end{equation*} 
	then \eqref{eqn:type_II} holds with respect to $C^{\star}$, so that we may apply Lemma \ref{lem:type_II}. In other words, we want to show $\epsilon^2 \geq 2b\sqrt{2N(C^*)/n^2} + C_n^2/n(C^*)^2$. By Assumption \ref{asmp:tail_decay} and the choice of $C^{\star}$, we have
	\begin{equation*}
	N(C^*) \leq (C^*)^{d/s}n = c^{d/s}(C_n n^{s/d})^{4d/(4s + d)}
	\end{equation*}
	and therefore
	\begin{equation*}
	2b\sqrt{\frac{N(C^*)}{n^2}} \leq \frac{2bc^{d/2s}}{n} (C_n n^{s/d})^{2d/(4s+d)}
	\end{equation*}
	Moving on to the second term, we have
	\begin{align*}
	\frac{C_n^2}{n(C^{\star})^2} & = \frac{C_n^2n^{2s/d}}{c^2n(C_nn^{s/d})^{8s/(4s+d)}} \\
	& = \frac{C_n^{2d/(4s + d)}n^{c^2(s/d)2d/(4s + d)}}{n} \\
	& = \frac{(C_n n^{s/d})^{2d/(4s + d)}}{c^2n}
	\end{align*}
	and therefore $\epsilon \geq 2b\sqrt{2N(C^*)/n^2} + C_n^2/n(C^*)^2$. As a result, by Lemma \ref{lem:type_II} for any $\beta \in \mathcal{S}^s_d(C_n)$ such that $\norm{\beta}/\sqrt{n} \geq \epsilon$, 
	\begin{equation*}
	\Ebb_{\beta}(1 - \phi_{C^{\star}}) \leq \frac{2}{b^2} + \frac{2}{b\sqrt{2N(C^{\star})}}.
	\end{equation*}
\end{proof}

@@

In the following result, we prove that for an appropriate choice of threshold $C$ and radius $r$, the test $\phi_C$ achieves (nearly) minimax-optimal rates, whenever $s > d/4$. (I.e whenever $\mathcal{W}^{s,2}(\mathcal{D})$ can be embedded into $L^4(\mathcal{D})$. Let
\begin{equation}
\label{eqn:C_star_continuous}
C^{\star} = \frac{\left(n^{1 + s/d}r^{d/2 + s}\right)^{4s/(4s + d)}}{n^{s/d}}.
\end{equation}
and suppose that $P$ be an absolutely continuous probability measure over $\D$ with density function $p$ bounded above and below by constants, i.e
\begin{equation*}
0 < p_{\textrm{min}} < p(x) < p_{\textrm{max}} < \infty, \quad \textrm{for all $x \in \mathcal{D}$.}
\end{equation*}

\begin{theorem}
	\label{thm:sobolev_testing_rate}
	Let $b \geq 1$ be a fixed constant, let $s = 1$, and let $4s < d$. For any sequence $r_n$ such that $(\log n/n)^{1/d}r_n \to \infty$, and $(n^{1 + s/d}r_n^{d/2 + s})^{4s/(4s + d)}n^{-s/d} \leq \sqrt{2}$ for all $n$, there exists a constant $c_1$ which depends only on $d$, $L$, $p_{\max}$, and $b$ such that
	\begin{equation}
	\label{eqn:sobolev_testing_rate_1}
	\mathcal{R}_{\epsilon}(\phi_{C^{\star}}; \mathcal{W}^{s,2}(\mathcal{D};L)) \leq \left(\frac{2}{b^2} + \frac{2}{b\sqrt{N(C^{\star})}}\right) + o(1)
	\end{equation}
	for every $\epsilon$ such that
	\begin{equation}
	\label{eqn:sobolev_testing_rate}
	\epsilon^2 \geq c_1 b \left(\frac{(b n^{1 + s/d}r^{d/2 + s})^{2d/(4s + d)}}{n}\right).
	\end{equation}
\end{theorem}
\begin{remark}
	Observe that when $4s > d$, the inequality $(n^{1 + s/d}r^{d/2 + s})^{4s/(4s + d)}n^{-s/d} \leq \sqrt{2}$ is satisfied whenever $r_n \leq n^{-3/(2d + 4s)} >> (\log(n)/n)^{1/d}$. In this regime, therefore, there exists a range of $r$ such that both conditions required in Theorem \ref{thm:sobolev_testing_rate} are satisfied. In particular, in this regime, choosing $r = \log(n)^{\alpha} (\log(n)/n)^{1/d}$ for any $\alpha > 0$, we have that the lower bound in \eqref{eqn:sobolev_testing_rate} becomes
	\begin{equation*}
	c_1 b (\log n)^{(1/d + \alpha)(d/2 + s)(2d/(4s + d))} n^{-4s/(4s + d)}
	\end{equation*}
	matching, up to log factors, the minimax rate for testing over Sobolev functions.
\end{remark}
\begin{remark}
	Many rates of nonparametric hypothesis testing exhibit an elbow when $4s < d$. In our particular setting, it can be shown that a naive test based on the statistic $\norm{z}_2^2$ has power for alternatives with norm $\norm{f}^2 \geq n^{-1/4}$, regardless of $s$ and $d$, for any $f \in L^4(\mathcal{D})$. 
\end{remark}

\subsection{Proof of Theorem \ref{thm:sobolev_testing_rate}}
Our goal is to upper bound
\begin{equation*}
\mathcal{R}_{\epsilon}(\phi_{C^{\star}}; W^{1,2}(\mathcal{D};L)) = \Ebb_{f = 0}(\phi_{C^{\star}}) + \sup_{f \in W^{1,2}(\mathcal{D};L): \norm{f}_{P,2} > \epsilon} \Ebb_{f}(1 - \phi_{C^{\star}})
\end{equation*}
By Lemma \ref{lem:type_I_error}, we immediately have $\Ebb_{f = 0}(\phi_{C^{\star}}) \leq 1/b^2$, and we turn to the worst-case type II error. Fix any $f \in W^{1,2}(\mathcal{D};L)$ such that $\norm{f}_2 > \epsilon$, and let $\beta$ be the length-$n$ random vector with $j$th entry $\beta_j = f(x_j)$. Consider the following events:
\begin{enumerate}[label=(E\arabic*)]
	\item 
	\label{event:discrete_sobolev_norm}
	Discrete Sobolev norm of $\beta$: There exists a constant $c_2$ which depends only on $p_{\max}$ and $d$ such that
	\begin{equation*}
	\norm{B^{(s)}\beta}_2^2 \leq c_2 b^2 n^2 r^{d + 2s} 
	\end{equation*}
	\item 
	\label{event:eigenvalue_tail_decay}
	Eigenvalue tail decay:
	\begin{equation*}
	N(C^{\star}) \leq n(C^{\star})^{d/s}.
	\end{equation*}
	\item 
	\label{event:l2_norm}
	$L_2$ norm of $\beta$:
	\begin{equation*}
	\frac{\norm{\beta}_2^2}{n} \geq \frac{1}{2}\epsilon^2.
	\end{equation*}
\end{enumerate}

Each of these events happen with high probability as $n \to \infty$.
\begin{lemma}[High Probability Events.]
	\label{lem:high_probability_events}
	\mbox{}

	\textbf{Discrete Sobolev norm.}
	There exists a constant $c_2$ which depends only on $p_{\max}$ and $d$ such that, with probability at least $1 - \frac{1}{b^2}$,
	\begin{equation}
	\label{eqn:discrete_sobolev_norm}
	\norm{B\beta}_2^2 \leq c_2 b^2 n^2 r^{d + 2}.
	\end{equation}

	\textbf{Eigenvalue tail decay.}
	Suppose the sequence of neighborhood graph radii $(r_n)$ satisfies
	\begin{itemize}
		\item $r(n/\log n)^{1/d} \to \infty$, and
		\item $r_n > \sqrt{2}n^{-1/(2d + 4s)}$ for all $n$.
	\end{itemize} 
	Then with probability tending to one as $n \to \infty$,
	\begin{equation}
	\label{eqn:eigenvalue_tail_decay}
	N(C^{\star}) \leq n(C^{\star})^{d/s}.
	\end{equation}

	\textbf{Norm of $\beta$.}
	There exists a constant $c_5$ which depends only on $s,d$, and $\mathcal{D}$ such that
	\begin{equation}
	\label{eqn:l2_norm}
	\frac{\norm{\beta}^2}{n} < \frac{\epsilon^2}{2}
	\end{equation}
	with probability at least $1  - 4c_5p_{\max}^4L^4/(n\epsilon^2) \to 0$ as $n \to \infty$. 
\end{lemma}

In the following subsections, we prove the various statements which make up Lemma \ref{lem:high_probability_events}. First, however, we show that Theorem \ref{thm:sobolev_testing_rate} is a simple consequence of Lemma \ref{lem:high_probability_events} along with the fixed graph testing results of Section \ref{sec:fixed_graph_testing}. Let $\mathcal{A}_f$ be the set of $X$ such that \ref{event:discrete_sobolev_norm}, \ref{event:eigenvalue_tail_decay}, and \ref{event:l2_norm} all occur, for the given choice of $f$. We have that for $C_n := \sqrt{c_2}bnr^{d/2 + s}$, the event \ref{event:discrete_sobolev_norm} implies $\beta \in \mathcal{S}_d^s(C_n)$. Therefore, by \ref{event:l2_norm},
\begin{equation}
\label{eqn:sobolev_testing_rate_2}
\Ebb_f(1 - \phi_{C^*}) \leq \sup_{\substack{\beta \in \mathcal{S}_d^{s}(C_n), \\ \norm{\beta}_2/n \geq \epsilon^2/2}} \Ebb_{\beta}(1 - \phi_{C^{\star}}) + \Pbb(\mathcal{A}_f).
\end{equation}
Observe the following: 
\begin{itemize}
	\item $C^{\star} = c_3(C_n n^{s/d})^{4s/(4s+d)}/n^{s/d}$, where $c_3 = (b c_2^{1/2})^{-1}$. 
	\item The event \ref{event:eigenvalue_tail_decay} is exactly \ref{asmp:tail_decay}, specialized to our choice of graph \textcolor{red}{$G_{n,r}$}, and 
	\item Letting $c_1 := 2c_2^{-2d/(4s + d)}\left(2bc_3^{d/2s} + c_3^{-2}\right)$, by \eqref{eqn:sobolev_testing_rate},
	\begin{equation*}
	\epsilon^2/2 \geq (2bc_3^{d/2s} + c_3^{-2}) \left(\frac{(C_n n^{s/d})^{2d/(4s + d)}}{n}\right)
	\end{equation*}
\end{itemize}
Therefore we may apply Corollary \ref{cor:critical_radius}, and obtain
\begin{equation*}
\sup_{\substack{\beta \in \mathcal{S}_d^{s}(C_n), \\ \norm{\beta}_2/n \geq \epsilon^2/2}} \Ebb_{\beta}(1 - \phi_{C^{\star}}) \leq \frac{2}{b^2} + \frac{2}{b\sqrt{N(C^{\star})}},
\end{equation*}
and along with \eqref{eqn:sobolev_testing_rate_2} and Lemma \ref{lem:high_probability_events}, this shows
\begin{equation*}
\Ebb_f(1 - \phi_{C^*}) \leq \frac{3}{b^2} + \frac{2}{b\sqrt{N(C^{\star})}} + o(1).
\end{equation*}

@@

\begin{lemma}
	\label{lem:sobolev_1_bound}
	For any $f \in W^{1,2}(\mathcal{D};L)$, and any $b \geq 1$, we have that there exists a constant $c_2 > 0$ which depends only on $d$ and $p_{\max}$ such that
	\begin{equation}
	\label{eqn:sobolev_1_bound}
	\norm{B\beta}_2^2 \leq L^2 b^2 c_2 n^2 r^{d + 2}
	\end{equation}
	with probability at least $1 - \frac{1}{b^2}$. 
\end{lemma}
\begin{proof}
	Observe that
	\begin{align*}
	\frac{1}{n^2}\Ebb(\beta^T L \beta) = \Ebb\left(\frac{1}{n^2} \sum_{i,j = 1}^{n} (\beta_i - \beta_j)^2 A_{ij}\right) & = \frac{(n - 1)}{n} \int_{\D} \int_{\D} (f(x) - f(y))^2\eta_r(x,y) \,dP(y) \,dP(x) \\
	& \leq p_{\max}^2 \frac{(n - 1)}{n} \int_{\D} \int_{\D} (f(x) - f(y))^2\eta_r(x,y) \,dy \,dx.
	\end{align*}
	We will show that for any $f \in \mathcal{W}^{1,2}(\D;L)$, there exists a constant $c_4$ which depends only on dimension $d$ such that
	\begin{equation}
	\label{eqn:mean_bound}
	\int_{\D} \int_{\D} (f(x) - f(y))^2\eta_r(x,y) \,dy \,dx \leq c_4 L^2 r^{d + 2}
	\end{equation}
	whence the desired result of \eqref{eqn:sobolev_1_bound} follows by Markov's inequality.

	We begin by dealing with complications due to the boundary of $\mathcal{D}$. Let $V$ be any bounded open set such that $\D \subset \subset V$. Note that as $\partial \D$ is $C^1$, by Theorem \ref{thm:evans_extension} there exists $g \in W^{1,2}(\Reals^d)$ such that
	\begin{enumerate}
		\item
		\label{eqn:evans_extension_1}
		$g = f$, $P$-almost-everywhere in $\D$
		\item 
		$g$ has support within $V$, and  
		\item 
		\label{eqn:sobolev_1_bound_2}
		$\norm{g}_{W^{1,2}(\Rd)} \leq C \norm{f}_{W^{1,2}(\D)}$ for a constant $c$ which depends only on $\mathcal{D}$.
	\end{enumerate}
	As a result of the first point,
	\begin{equation}
	\label{eqn:sobolev_1_bound_1}
	\int_{\D} \int_{\D} (f(x) - f(y))^2\eta_r(x,y) \,dy \,dx \leq \int_{\Rd} \int_{\Rd} (g(x) - g(y))^2\eta_r(x,y) \,dy \,dx.
	\end{equation}

	Next, we smooth $g$, so that we may work with ordinary partial derivatives.
	We let $\kappa \in C^{\infty}(\Rd)$ be given by
	\begin{equation*}
	\kappa(x) :=
	\begin{cases}
	C \exp \left\{\frac{1}{\norm{x}^2 - 1}\right\}& \quad \textrm{if $\norm{x}_2 \leq 1$} \\
	0 & \quad \textrm{if $\norm{x}_2 \geq 1$}
	\end{cases}
	\end{equation*}
	where the normalizing constant $C > 0$ is chosen so that $\int_{\Rd} \eta dx = 1$. Let $\kappa_r(x) := (1/r^d) \kappa(x/r)$. Then, the mollification of $g$ by $\kappa_r$ is given by
	\begin{align*}
	g^r & := g \ast \eta_r \\
	& = \int_{\Rd} \eta_r(x - y) g(y) dy
	\end{align*}
	(Refer to \citep{evans10}, Appendix C, Theorem 7 for a proof that $g^r \in C^{\infty}(\Rd)$.)
	Adding and subtracting within \eqref{eqn:sobolev_1_bound_1}, we have
	\begin{align}
	\int_{\Rd} & \int_{\Rd} (g(x) - g(y))^2\eta_r(x,y) \,dy \,dx \\
	& \leq 3 \int_{\Rd} \int_{\Rd} \bigl((g(x) - g^r(x))^2 + (g^r(x) - g^r(y))^2 + (g^r(y) - g(y))^2\bigr)\eta_r(x,y) \,dy \,dx \nonumber \\
	& = 6 \int_{\Rd} \int_{\Rd} \bigl((g(y) - g^r(y))^2 \eta_r(x,y) \,dy \,dx + 2 \int_{\Rd} \int_{\Rd} \bigl((g^r(x) - g^r(y))^2 \eta_r(x,y) \,dy \,dx \label{eqn:sobolev_1_bound_5}
	\end{align}
	We deal with each summand individually, beginning with the first one. Let $\nu_d = \pi^{d/2}/\Gamma(d/2 + 1)$ denote the volume of a ball with unit radius in $\Rd$. Then, we have
	\begin{align}
	\int_{\Rd} \int_{\Rd} \bigl((g(y) - g^r(y))^2 \eta_r(x,y) \,dy \,dx & = \int_{\Rd} \int_{B(x,r)} \bigl((g(y) - g^r(y))^2\,dy \,dx \nonumber \\
	& = \int_{\Rd} \int_{B(y,r)} \bigl((g(y) - g^r(y))^2\,dx \,dy \tag{Tonelli's Theorem} \nonumber \\
	& = \nu_d r^d \int_{\Rd}\bigl((g(y) - g^r(y))^2 \,dy \\
	& \leq \nu_d r^{d + 2} \int_{\Rd} \norm{\nabla g(y)}^2 \,dy \label{eqn:sobolev_1_bound_4}
	\end{align}
	where the last line follows from Lemma \ref{lem:poincare_mollify}.

	We now turn our attention to the second summand. Note that as $g^r \in C^{\infty}(\Rd)$, we may apply Theorem \ref{thm:taylor_expansion} and obtain
	\begin{align*}
	(g^r(x) - g^r(y))^2 & = \left(\int_{0}^{1} \nabla g^r(x + t(y - x)) \cdot (y - x) \,dt\right)^2 \\
	& \leq \int_{0}^{1} \bigl(\nabla g^r(x + t(y - x)) \cdot (y - x)\bigr)^2 \,dt  \tag{Jensen's inequality} \\
	& \leq \norm{y - x}^2 \int_{0}^{1} \norm{\nabla g^r(x + t(y - x))}^2 \,dt. \tag{Cauchy-Schwarz inequality}
	\end{align*}
	As a result, we have
	\begin{align*}
	\int_{\Rd} \int_{\Rd} \bigl((g^r(x) - g^r(y))^2 \eta_r(x,y) \,dy) \,dx & \leq \int_{\Rd} \int_{\Rd} \norm{y - x}^2  \int_{0}^{1} \norm{\nabla g^r(x + t(y - x))}^2 \eta_r(x,y) \,dt \,dy \,dx \\
	& \leq r^{2} \int_{\Rd} \int_{\Rd} \int_{0}^{1} \norm{\nabla g^r(x + t(y - x))}^2 \eta_r(x,y) \,dt \,dy \,dx \\
	& = r^{2} \int_{\Rd} \int_{0}^{1} \int_{\Rd} \norm{\nabla g^r(x + t(y - x))}^2 \eta_r(x,y) \,dx \,dt \,dy \\
	& = r^{2} \int_{\Rd} \int_{0}^{1} \int_{\Rd} \norm{\nabla g^r(x + tz)}^2 \eta_r(z) \,dx \,dt \,dz \tag{$z = y - x$}
	\end{align*}

	where we write $\eta_r(z) = \mathbf{1}(\norm{z} \leq r)$ in an abuse of notation. Next, we note that
	\begin{equation*}
	\int_{\Rd} \norm{\nabla g^r(x + tz)}^2 \,dx = \int_{\Rd} \norm{\nabla g^r(x)}^2 \,dx \leq \int_{\Rd} \norm{\nabla g(x)}^2 \,dx
	\end{equation*}
	with the inequality following from Lemma \ref{lem:gradient_mollify_commute}. Therefore,
	\begin{align}
	r^{2} \int_{\Rd} \int_{0}^{1} \int_{\Rd} \norm{\nabla g^r(x + tz)}^2 \eta_r(z) \,dx \,dt \,dz & \leq r^{2} \int_{\Rd} \eta_r(z) \int_{0}^{1} \int_{\Rd} \norm{\nabla g(x)}^2 \,dx  \,dt \,dz \nonumber \\
	& = \nu_d r^{2 + d} \int_{\Rd} \norm{\nabla g(x)}^2 \,dx. \label{eqn:sobolev_1_bound_3}
	\end{align}
	By \eqref{eqn:sobolev_1_bound_5}, \eqref{eqn:sobolev_1_bound_4} and \eqref{eqn:sobolev_1_bound_3}, we have that 
	\begin{equation*}
	\int_{\Rd} \int_{\Rd} (g(x) - g(y))^2 \eta_r(x,y) \,dx \,dy \leq 9 \nu_d r^{d + 2} \int_{\Rd} \norm{\nabla g(x)}_2^2 \,dx
	\end{equation*}
	Then by \eqref{eqn:sobolev_1_bound_2}, $\int_{\Rd} \norm{\nabla g(x)}_2^2 \,dx \leq c \int_{\D} \norm{\nabla f(x)}_2^2 \,dx \leq c L^2 $ where $c$ is a constant depending only on $\D$. So the desired result of \eqref{eqn:sobolev_1_bound_1} follows.
\end{proof}

\subsection{Proof of \eqref{eqn:eigenvalue_tail_decay}.}

\begin{theorem}
	\label{thm:spectral_decay}
	Let $r \to 0$ as $n \to \infty$ sufficiently slowly so that $r(\log n/n)^{1/d} \to \infty$. Then, for each $s > 0$ and $C \leq \sqrt{2}$,
	\begin{equation}
	\label{eqn:spectral_decay}
	N(C) \leq n C^{d/s}.
	\end{equation} 
	with probability tending to one as $n \to \infty$. 
\end{theorem}

Before we prove Theorem \ref{thm:spectral_decay}, we observe that, whenever $4s > d$, the choice of $C^{\star}$ by \eqref{eqn:C_star_continuous} along with the requirement that $r_n < \sqrt{2}(n^{-3/(2d + 4s)})$ implies $C^{\star} < \sqrt{2}$ for all $n$. Therefore, Theorem \ref{thm:spectral_decay} implies \eqref{eqn:eigenvalue_tail_decay}, the desired result.

To prove Theorem \ref{thm:spectral_decay}, we will make use of a grid graph $\widetilde{G}$ on points within $\mathcal{D}$, whose spectral properties are very well-understood. Let $\xi$ be the set of evenly spaced lattice points over $\mathcal{D}$; formally $\xi = \set{k/n: k \in [\ell]^d}$ where $\ell = n^{1/d}$, and we define $[\ell]^d = \set{(\ell_1,\ldots,\ell_d): \ell_k \in [\ell] ~\textrm{for each}~ \ell_k}$. Then, let the grid graph over $\xi$ be given by $\wt{G} = (\wt{V},\wt{E})$, where $\wt{V} = \xi$ and $(\xi_k, \xi_{k'})$ is in $\wt{E}$ if $\norm{\xi_k - \xi_{k'}}_1 = 1/\ell$.

Let $\wt{L}$ be the Laplacian of $\wt{G}$, and let $\wt{\lambda_1} \leq \ldots \leq \wt{\lambda}_n$ be the ordered eigenvalues of $\wt{L}$. Write $\wt{N}(C) = \#\set{k: \wt{\lambda}_k^s \leq C^2}$. We have that the desired scaling rate \eqref{eqn:spectral_decay} holds with respect to the grid graph $\wt{G}$.

\begin{lemma}
	\label{lem:spectral_decay_grid}
	For each $s$ and every $C \leq \sqrt{2}$, we have
	\begin{equation}
	\label{eqn:spectral_decay_grid}
	\wt{N}(C) \leq 2^d\big(n C^{d/s} + 1)
	\end{equation}
\end{lemma}
\begin{proof}
	It will be sufficient to show that 
	\begin{equation}
	\label{eqn:spectral_decay_grid_1}
	\lambda_k^s \leq C^2 \Rightarrow \floor{k^{1/d}}^d \leq C^{d/s}n
	\end{equation}
	To show this, observe that for any $\tau \in \mathbb{N}$ and $k = \tau^d$, we have
	\begin{equation*}
	\lambda_k \geq 4 \sin^2 \left(\frac{\pi k^{1/d}}{2n^{1/d}}\right) \geq \frac{\pi^2 k^{2/d}}{4 n^{2/d}} \wedge 2
	\end{equation*}
	Therefore, if $\lambda_k^s \leq C^2$ and $C \leq \sqrt{2}$, this implies
	\begin{equation*}
	\frac{\pi^{2s} k^{2s/d}}{4^s n^{2s/d}} \leq C^{2}
	\end{equation*}
	and rearranging, we obtain
	\begin{equation*}
	k \leq \frac{C^{d/s} 2^d n}{\pi^d} \leq C^{d/s}n
	\end{equation*}	
	If $k^{1/d}$ is not a natural number, applying the same argument to $k' = \floor{k^{1/d}}^d$ yields \eqref{eqn:spectral_decay_grid_1}.
\end{proof}

In light of Lemma \ref{lem:spectral_decay_grid}, to prove Theorem \ref{thm:spectral_decay} it is sufficient to show that $\wt{L} \preceq L$, since by the Courant-Fischer min-max theorem, the ordering $\wt{L} \preceq L$ implies that $\wt{\lambda}_k \leq \lambda_k$ for all $k \in [n]$. The next result details the conditions under which this ordering holds. This condition will be stated with respect to the min-max matching distance between $\xi$ and $X$, i.e. the minimum over all bijections $T: \xi \to X$ such that
\begin{equation*}
\min_{T} \max_{i \in [n]} \abs{T^{-1}(x_i) - x_i} 
\end{equation*}
